\documentclass[12pt,a4paper]{article}
\usepackage[left=0.7in,right=0.7in,top=0.7in,bottom=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}

\usepackage{array}
\usepackage{longtable}
\setlength{\LTpre}{-2pt}
\setlength{\LTpost}{0pt}

\usepackage{fontawesome5}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=NavyBlue,
    linkcolor=blue,
}

\usepackage[dvipsnames]{xcolor}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% \usepackage[T1]{fontenc}
% \usepackage{gentium}

% \usepackage{fontspec}

\usepackage{helvet}

\pagenumbering{gobble}

% Adjust the section titles
\titleformat{\section}{\normalfont\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

% \noindent
% \begin{center}
% \textbf{\LARGE Rahul Ramaka} \\
% E-mail: \texttt{rahulathreya@yahoo.com} \\
% Telephone: +44 7763 331895 \\
% Portfolio: {\texttt{https://muffpy.github.io/}}
% \end{center}

\noindent
{\Large\textbf{Rahul Ramaka}} \hfill Last updated: August, 2024
\noindent\rule{\textwidth}{2pt}\smallskip

\noindent
\faEnvelope\  \href{mailto:rahulathreya@yahoo.com}{rahulathreya@yahoo.com} \hfill \faGlobe\ \href{https://muffpy.github.io/}{muffpy.github.io}

\noindent
\faPhone\ +44 7763 331895 \hfill \faGithub\ \href{https://github.com/muffpy}{github.com/muffpy}

\small

\section{Summary}
Accomplished Full-stack Software Engineer with a First-Class Honours BSc in Computer Science from King's College London. Professional internship experience at Amazon Web Services (AWS), Prime Video Studios, and Snapchat, developing complex, scalable applications including cloud-based microservices, real-time systems, and machine learning systems. Proficient in Python, C++, Java, and JavaScript, with a strong foundation in data structures \& algorithms and systems programming.

\vspace{-3mm}

\section{Skills}

\begingroup
\renewcommand{\arraystretch}{1.3} % Default value: 1
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, C++20, C, Java, JavaScript, Scala, Go, \LaTeX, Bash \\
Database & MySQL, PostgreSQL, MongoDB, Elasticsearch \\
Web & Node.js, Express, TypeScript, Django, HTML, CSS \\
Tools & Git, Docker, k8s, Make, CMake, perf, gdb/lldb, gRPC, OpenSSL \\
Systems & AWS, TCP/IP, TensorFlow, PyTorch, GNU/Linux

% \\
% Soft Skills & Efficiency Management, Teamwork, Communication, Accountability
% \\
\end{tabular}
\endgroup

\vspace{-2mm}


% \begin{flushleft}
% \textbf{Operating system level software:} syscalls, signals, pipes, mmap, locks, page tables, caching, containers (Docker, k8s), distributed computing (gRPC, KVS, AFS, Blockchain)
% \end{flushleft}

% \begin{flushleft}
% \textbf{Networking:} socket programming, TCP/IP programming, network adaptors and interfaces
% \end{flushleft}

\section{Experience}

\begin{longtable}{p{\textwidth}}
% \textbf{2023-24} & \textbf{Independent Consulting \& Professional Skill Development} \vspace{1pt}
%        \begin{itemize}[itemsep=-1.5mm,topsep=0pt,partopsep=0pt,leftmargin=5mm]
%         \item Worked on personal software projects: \hyperref[sec:projects]{lightdb}, \hyperref[sec:projects]{netstackxx}, \hyperref[sec:projects]{libdeep}, \hyperref[sec:projects]{mrgo}.
%         \item
%         \item Launched an independent fitness consulting service and acquired client base through referrals and social media marketing.
%        \end{itemize} \\
\textbf{PLSV Group, University of Cambridge} \hfill \small{2023-23} \\
       Research Intern \vspace{1pt}
       \begin{itemize}[itemsep=-2mm,topsep=0pt,partopsep=0pt,leftmargin=5mm]
        \item Collaborated on the DIADEM project supported by EPSRC, Arm and Pernosco to improve LLVM compiler-generated debugging metadata coverage.
        \item \textbf{Informed future research} efforts by showing that the CPU bottleneck in metadata generation is the reflection library, not OS-level congestion or the registers itself.

       \end{itemize} \vspace{2mm}
\textbf{Amazon Web Services (AWS), Amazon} \hfill \small{2022-22}  \\
       SDE Intern - AWS ML \vspace{1pt}
       \begin{itemize}[itemsep=-2mm,topsep=0pt,partopsep=0pt,leftmargin=5mm]
        \item Designed and implemented optimized ML framework to cluster  Cloudformation graphs and worked on new capabilities as microservices for the team’s flagship conversational AI agent.
        % \item Designed a (3x) fast, metric-based, localized CloudWatch aggregation protocol.
        \item Built Python-based dashboard app that accelerated PM screening and instantly visualized product’s unique engineering pipeline and development workflow and reduced experiment time \textbf{10×}.
        \item Improved CI/CD infra, increasing successful deployments to the global fleet of \textbf{9M servers}.
        \item Participated in oncall, handled customer tickets, investigated \& fixed critical software defects.

% \item Built a dockerized dashboard app which is deeply integrated into debugging, testing and benchmarking workflows, boosting development speed by 45\%.
% \item Maintained overview documents of the MLOps system to facilitate knowledge transfer and help new hires learn about the system.

       \end{itemize} \vspace{2mm}
\textbf{Department of Informatics, NMES, King's College London} \hfill \small{2021-22} \\
       Teaching Associate: C++ programming (2021) and Operating Systems (2022) 
       \begin{itemize}[itemsep=-2mm,topsep=2pt,partopsep=0pt,leftmargin=5mm]
        \item Head TA for the Operating Systems (2022) module: tutored students in OS development, C/C++ programming and Unix.
        \item Cut xv6 (educational) OS image build time \textbf{2x} with a CI pipeline using Packer and QEMU.
       \end{itemize} \vspace{2mm}
\textbf{Video Quality Analysis, Prime Video \& Amazon Studios} \hfill \small{2021-21} \\
       SDE Intern - PV VQA \vspace{1pt}
       \begin{itemize}[itemsep=-2mm,topsep=0pt,partopsep=0pt,leftmargin=5mm]
        \item Created a livestream player with real-time notifications of A/V defects detected using computer vision models trained on synthetic media, replacing third-party legacy software and \textbf{cutting overhead}.
        % \item Implemented microservice orchestration workflows between media conversion and defect detection services using AWS Step Functions and S3.
        % \item Implemented a prototype audio codec in C++ (native code), including several optimized DSP components.
        \item Contributed to AWS Elemental Media Distribution Services: MediaConnect, MediaStore, Kinesis.
        \item Contributed to building a service emulator for evaluating microservice orchestration workflow (AWS Step Functions + S3) latency and resource cost at scale, increasing existing performance by \textbf{3x}.
%         \item Discovered that networking stack features for improving CPU use through offloading and aggregation —
% e.g., generic receive offload, interrupt coalescing, delayed ACKs — 
        \item Investigated the performance accuracy and efficiency of pre-trained defect detector models against self-supervised models when fine-tuned on synthetic fine-grained audio/video.
        % \item Built a light weight client supporting source-side deduplication for the company’s distributed filesystem for backups
       \end{itemize} \\
\textbf{Mobile Messaging, Snapchat Engineering} \hfill \small{2020-20} \\
       Software Engineer Intern \vspace{1pt}
       \begin{itemize}[itemsep=-1mm,topsep=0pt,partopsep=0pt,leftmargin=5mm]
        \item Worked on cross-platform mobile messaging across Android and iOS.
        \item Contributed to the C++ cross-language interface (Djinni) to the platform-specific code.
        \item Implemented key features, including a cache-aware memory management framework and the high-level synthesis (HLS) protocol of Djinni; will be \textbf{deployed on millions} of datacenter servers
       \end{itemize}
\end{longtable}

\vspace{-6mm}

\section{Education}
\begin{longtable}{p{15cm}p{2cm}@{}}
\textbf{Department of Informatics, King's College London} & \small{2019-22} \\
         BSc Hons., Computer Science, \textit{\textcolor{blue}{First-Class Honours.}}

          \textcolor{YellowOrange}{Springer Nature Prize} (distinguished performance in second year studies.) \vspace{3mm} \\
\textbf{DPS International School Singapore} & \small{2016-18}  \\
         Highest score in academic year: A Level (A* A* A* A*) and AS Level (AAAA). Gold Scholar Badge and Excellence Scholarship (S\$6500).
\end{longtable}


\section{Projects}
\label{sec:projects}

\begin{longtable}{p{15cm}p{2cm}@{}}
\textbf{libdeep} \href{https://github.com/muffpy/libdeep}{\faGithub } 
% {\footnotesize C++, Python}
\vspace{1pt}
\begin{itemize}[itemsep=-2mm,topsep=0pt,leftmargin=5mm]
\item Wrote automatic differentiation tools for various implemented functions. Support parameterized layers and loss functions.
\item Implement GPU/CPU-aware NDarray library achieving comparable performance to numpy (2-3x slower).
\end{itemize}
& 2024 \\

\textbf{LightDB} \href{https://github.com/muffpy/lightdb}{\faGithub } 
% {\footnotesize C++} 
\vspace{1pt}
\begin{itemize}[itemsep=-2mm,topsep=0pt,leftmargin=5mm]
\item Implements key components of a traditional RDBMS including Buffer Pool Manager (for memory management), Hash Index (storage engine), Query Executors \& Query Optimizer (operators \& optimizer), and Concurrency Control.
\end{itemize}
& 2023-24 \\

\textbf{Netstack(xx)} \href{https://github.com/muffpy/netstackxx}{\faGithub } 
% {\footnotesize C++}  
\vspace{1pt}
\begin{itemize}[itemsep=-2mm,topsep=0pt,leftmargin=5mm]
\item Implement TCP protocol: assembler, receiver, sender; network interface following ARP (address resolution protocol) and IP routing in C++.
\end{itemize}
& 2023-24 \\

\textbf{Common Architectures} \href{https://muffpy.github.io/assets/home/commonarch_press.pdf}
{\faFilePdf} 
% {\footnotesize Python, JavaScript, Django, AWS}
\vspace{1pt}
\begin{itemize}[itemsep=-2mm,topsep=0pt,leftmargin=5mm]
\item In collaboration with Amazon DevOpsGuru team in London and Germany.
\end{itemize}
& 2022 \\

\textbf{liballocs-gc}  
% {\footnotesize Python, C, C++}
\vspace{1pt}
\begin{itemize}[itemsep=-2mm,topsep=0pt,leftmargin=5mm]
\item In collaboration with my undergraduate supervisor Dr Stephen Kell.
\item \href{https://github.com/muffpy/liballocsgc}{Code}, \href{https://drive.google.com/file/d/1_Y17HzvwnW6imM27xlZhJmW0-XSgMreF/view}{paper}, and liballocs \href{https://www.humprog.org/~stephen/research/liballocs/}{documentation}.
\end{itemize}
& 2022 \\

\textbf{Fun-compiler} \href{https://github.com/muffpy/funlang}{\faGithub }  
% {\footnotesize Scala}
\vspace{1pt}
\begin{itemize}[itemsep=-2mm,topsep=0pt,leftmargin=5mm]
\item Built an LLVM-backed FUN language compiler in Scala which uses a CPS (continuous passing style) format-compliant intermediate K-language.
\end{itemize}
& 2021-22
% \begin{itemize}[leftmargin=0em]
%     % \item [] \href{https://github.com/muffpy/mrgo}{\textbf{mrgo}} a MapReduce implementation in Golang
%     \item  [] \href{https://muffpy.github.io/assets/home/commonarch_press.pdf}{\textbf{common-archs}} 
%     \item [] \href{https://github.com/muffpy/liballocsgc}{\textbf{liballocsgc}} 
%     \item [] \href{https://github.com/muffpy/funlang}{\textbf{funlang}} 
\end{longtable}
\vspace{-5mm}
% \section{Core Skills}
% \begin{tabular}{p{0.45\textwidth} p{0.45\textwidth}}
% \textbf{Client communication} & \textbf{Continuous learning} \\
% Effectively convey technical ideas to non-technical audiences and practise active listening to meet client needs. & 

% Proactively study and apply new knowledge across disciplines, adapting quickly to emerging technologies and methodologies. \\ \\
% \textbf{Efficiency Management} & \textbf{Analytical Problem-solving} \\
% Implement data-driven strategies and time management techniques to enhance personal and team efficiency. & 

% Apply analytical thinking and logical reasoning to break down complex challenges into manageable components. \\
% \end{tabular}

\section{Referees}

\begin{flushleft}
\href{https://www.kcl.ac.uk/people/stephen-kell}{\textbf{Dr Stephen Kell}}, Lecturer in Computer Science, King's College London

\href{https://www.kcl.ac.uk/people/laurence-tratt}{\textbf{Prof. Laurence Tratt}}, Professor of Software Development, King's College London

\href{mailto:oswaldhs@amazon.co.uk}{\textbf{Oswaldo Hernandez}}, Software Development Manager, Amazon Web Services
\end{flushleft}

\end{document}
