\documentclass[11pt,a4paper]{article}
\usepackage{geometry}
\geometry{
	paper=a4paper, % Paper size, change to letterpaper for US letter size
	top=2.25cm, % Top margin
	bottom=2cm, % Bottom margin
	left=4cm, % Left margin
	right=3.5cm, % Right margin
	headheight=0.75cm, % Header height
	footskip=1cm, % Space from the bottom margin to the baseline of the footer
	headsep=0.75cm, % Space from the top margin to the baseline of the header
	%showframe, % Uncomment to show how the type block is set on the page
}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\usepackage{fontawesome5}
\usepackage{hyperref}
\definecolor{mypink3}{cmyk}{0, 0.7808, 0.6029, 0.2312}

\hypersetup{
    colorlinks=true,
    urlcolor=BrickRed
}
\definecolor{light-grey-pink}{HTML}{fffafb}
\pagecolor{light-grey-pink}

% \usepackage[utf8]{inputenc}
% \usepackage[T1]{fontenc}
% \usepackage{mathptmx}

\usepackage{fontspec}
\setmainfont{MinionPro}[
  UprightFont = *-Regular,
  ItalicFont = *-It,
  BoldFont = *-Bold,
  BoldItalicFont = *-BoldIt,
  Extension = .ttf
]
\newfontfamily\myfont{adobehebrew-regular.otf}

\pagenumbering{gobble}

% Adjust the section titles
\titleformat{\section}{\scshape\raggedright\large}{}{0em}{}[]
\let\oldtitleline\titleline
\renewcommand{\titleline}{\oldtitleline*}
\setlength{\titlewidth}{0.05\textwidth}

\usepackage{marginnote} % Required to output text in the margin

\newcommand{\years}[1]{\marginnote{\footnotesize\myfont #1}} % New command for adding years to the margin
\renewcommand*{\raggedleftmarginnote}{} % Left-align the years in the margin
\setlength{\marginparsep}{20pt} % Move the margin content closer to the text
\reversemarginpar % Margin text to be output into the left margin instead of the default right margin

\begin{document}

\small

\noindent
{\huge\scshape Rahul Ramaka} \vspace{0.5mm} \\ 
{\large \textit{Curriculum vitæ} {\myfont\normalsize (3rd Sep 2024)}} \medskip \\

\noindent
\begin{tabular}{@{}p{7.5cm}p{5cm}}
    \textbf{M.Sc. Student} & \faEnvelope \quad \href{mailto:rahulathreya@yahoo.com}{rahulathreya@yahoo.com\textsuperscript{\tiny\faExternalLink*}} \\
    Department of Computer Science & \faGithub \quad \href{https://github.com/muffpy}{github.com/muffpy\textsuperscript{\tiny\faExternalLink*}} \\
    Clare Hall College & \faGlobe \quad \href{https://muffpy.github.io/}{Portfolio\textsuperscript{\tiny\faExternalLink*}}\\
    University College London, UK & \faPhone \quad \href{tel:07763331895}{+44 7763 331895}
\end{tabular}

\vspace{3mm}

\section{Education}
\textbf{King's College London, UK} \smallskip \\
\years{2024-2025} M.Sc. (Hons.) in Advanced Computer Science. \smallskip \\
\years{2019-2022} B.Sc. (Hons.) in Computer Science. \\ 
{\myfont 1st}-Class Honours. Springer Nature Prize (distinguished performance in second-year studies.) \\
\textit{Precise and Automatic Memory Management using liballocs}; supervisor: Dr Stephen Kell. \medskip \\ 
\years{2016-2018} \textbf{DPS International School, Singapore} \\
\textit{A Level} (A* A* A* A*). \textit{AS Level} (AAAA). Gold Scholar Badge and Excellence Scholarship (S\$6500).

\section{Work Experience}
% \begin{longtable}{@{\hspace{0.5cm}}p{2cm}p{14cm}@{}}
\years{2023-24} \textbf{Independent Consulting \& Professional Skill Development} \vspace{1pt}
    \begin{itemize}[itemsep=-1.5mm,topsep=0pt,partopsep=0pt,leftmargin=5mm]
    \item Strategic break from corporate roles to focus on personal development.
    \item Gained expertise in exercise and nutritional sciences through self-study and application, aiming to optimize cognitive performance and work-life balance. \medskip
    \end{itemize}
\years{2023-23} \textbf{PLSV Group, Computer Laboratory, University of Cambridge} \\
    Research Intern \vspace{1pt}
    \begin{itemize}[itemsep=-1mm,topsep=0pt,partopsep=0pt,leftmargin=5mm]
    \item Collaborated on the DIADEM project supported by EPSRC, Arm and Pernosco.
    % to improve LLVM compiler-generated debugging metadata coverage.
    \item \textbf{Informed future research} efforts by showing that the CPU bottleneck in metadata generation is the reflection library, not OS-level congestion or the registers itself. \medskip
    \end{itemize}
    \years{2022-22} \textbf{Amazon Web Services (AWS), Amazon} \\
    SDE Intern \vspace{1pt}
    \begin{itemize}[itemsep=-1mm,topsep=0pt,partopsep=0pt,leftmargin=5mm]
     \item Designed and implemented optimized ML framework to cluster Cloudformation graphs.
     % \item Built new capabilities as microservices for the team’s flagship conversational AI agent.
     % \item Designed a (3x) fast, metric-based, localized CloudWatch aggregation protocol.
     \item Built Python-based dashboard app that \textbf{accelerated PM screening} and instantly visualized product’s unique engineering pipeline and \textbf{boosted development speed}.
     \item Improved CI/CD infra, increasing successful deployments to the global fleet of \textbf{9M servers}.
     \item Participated in oncall, handled customer tickets, investigated \& fixed critical software defects.\medskip
    \end{itemize}
    \years{2021-21} \textbf{Video Quality Analysis, Prime Video \& Amazon Studios} \\
    SDE Intern \vspace{1pt}
    \begin{itemize}[itemsep=-1mm,topsep=0pt,partopsep=0pt,leftmargin=5mm]
     \item Created a livestream player with real-time A/V defect alarms and thereby \textbf{cutting overhead} of third-party legacy software.
     % \item Implemented microservice orchestration workflows between media conversion and defect detection services using AWS Step Functions and S3.
     % \item Implemented a prototype audio codec in C++ (native code), including several optimized DSP components.
     \item Contributed to AWS Elemental Media Services: MediaConnect, MediaStore, Kinesis.
     \item Contributed to building a service emulator for evaluating AWS microservice orchestration latency and billing, increasing existing performance by \textbf{3x}.
     \item Investigated the performance accuracy and efficiency of pre-trained defect detector CV models against self-supervised models fine-tuned on synthetic fine-grained audio/video.\medskip
    \end{itemize}
    \years{2020-2020} \textbf{Mobile Messaging, Snapchat Engineering} \\
    Software Engineer Intern \vspace{1pt}
    \begin{itemize}[itemsep=-1mm,topsep=0pt,partopsep=0pt,leftmargin=5mm]
     \item Worked on cross-platform mobile messaging across Android and iOS.
     \item Contributed to the C++ cross-language interface (Djinni) to the platform-specific code.
     \item Implemented key features, including a cache-aware memory management framework and the high-level synthesis (HLS) protocol of Djinni; \textbf{deployed on millions} of datacenter servers.
    \end{itemize}

    \section{Projects}

    \begin{itemize}[leftmargin=0em]
        \item [] \href{https://github.com/muffpy/libdeep}{\textbf{libdeep}} a PyTorch-like deep learning library in C++/Python
        \item [] \href{https://github.com/muffpy/lightdb}{\textbf{lightdb}} a lightweight disk-oriented relational database in C++
        \item [] \href{https://github.com/muffpy/netstackxx}{\textbf{netstackxx}} rewriting the Linux networking protocol stack in C++
        \item [] \href{https://github.com/muffpy/mrgo}{\textbf{mrgo}} a MapReduce implementation in Golang
        \item  [] \href{https://muffpy.github.io/assets/home/commonarch_press.pdf}{\textbf{common-archs}} clustering AWS Cloudformation graphs
        \item [] \href{https://github.com/muffpy/liballocsgc}{\textbf{liballocsgc}} a semi-precise C/C++ garbage collector extension for liballocs
        \item [] \href{https://github.com/muffpy/funlang}{\textbf{funlang}} an LLVM backed FUN language compiler in Scala
    \end{itemize}

\section{Technical Skills}

\begingroup
\renewcommand{\arraystretch}{1.3} % Default value: 1
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, C++20, C, Java, JavaScript, Scala, Go, \LaTeX \\
Database & MySQL, PostgreSQL, MongoDB, Elasticsearch \\
Web & Node.js, Express, TypeScript, Django, HTML, CSS \\
Tools & Docker, k8s, Make, CMake, perf, gdb/lldb, gRPC, OpenSSL \\
Systems & AWS, TensorFlow, PyTorch, GNU/Linux, TCP/IP
\end{tabular}
\endgroup

    \section{Core Skills}
    \begin{tabular}{p{0.45\textwidth} p{0.45\textwidth}}
    \textbf{Client communication} & \textbf{Continuous learning} \\
    Effectively convey technical ideas to non-technical audiences and practise active listening to meet client needs. & 
    
    Proactively study and apply new knowledge across disciplines, adapting quickly to emerging technologies and methodologies. \\ \\
    \textbf{Efficiency Management} & \textbf{Analytical Problem-solving} \\
    Implement data-driven strategies and time management techniques to enhance personal and team efficiency. & 
    
    Apply analytical thinking and logical reasoning to break down complex challenges into manageable components. \\
    \end{tabular}
    
    
    \section{Referees}
    
    \begin{flushleft}
    \href{https://www.kcl.ac.uk/people/stephen-kell}{\textbf{Dr Stephen Kell}}, Lecturer in Computer Science, King's College London
    
    \href{https://www.kcl.ac.uk/people/laurence-tratt}{\textbf{Prof. Laurence Tratt}}, Professor of Software Development, King's College London
    
    \href{mailto:oswaldhs@amazon.co.uk}{\textbf{Oswaldo Hernandez}}, Software Development Manager, Amazon Web Services
    \end{flushleft}
    
\end{document}